---
title: "Plotly"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

This page is about making some plotly examples.

```{r setup, message=FALSE}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```


NYC Airbnb data


* The mutate line is saying that a 10 rating should be 5 stars
* Keeping the variables we care about 
* We only want a subset of what we're interested in, it's a big data set to run in the background so we filter

```{r}
data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>%
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) %>%
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500) %>% 
  drop_na(rating)
```


Plotly scatterplot:

* The \ puts this on a new line

```{r}
nyc_airbnb %>%
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) %>% 
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)
```

Plotly boxplot:

* Mutate to put things in order with factor reorder, neighborhood in order of price

```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```




